MinCall --- MinION end2end deep learning basecaller

### 2017-06-30 paper/main.tex
Update

Training the model is the minimization of previously described CTC loss. It was done using Adam \cite{adam} with default parameters, and minibatch size 8. To prevent gradients exploding on bad inputs, they were clipped to a range [-2, 2]. We observed no overfitting due to large dataset size.

>>>>

Training the model is the minimization of previously described CTC loss. It was done using Adam~\cite{adam} with default parameters, and exponentially decaying learning rate starting from 1e-3 and decay rate of 5e-6 over 100k steps\footnote{We use tf.train.exponential\_decay where current learning rate, lr is $lr=\text{initial\_lr} \cdot \text{decay\_rate}^\frac{\text{global\_step}}{\text{decay\_step}}$} and minibatch size 8. To prevent gradients exploding on bad inputs, they were clipped to a range [-2, 2]. We observed no overfitting due to large dataset size.
